Modelling last glacial cycle ice dynamics in the Alps

### 2017-08-18 articles/cycle/alps-cycle.tex
Update figure captions.

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_timing}}
      \caption{%
        \textbf{(a)} Timing of the LGM given by the
        modelled age (colour mapping) and value (200\,m contours) of maximum
        surface elevation throughout the entire simulation.
        \textbf{(b)} Temperature offset time-series from the EPICA ice core
        used as palaeo-climate forcing for the ice flow model (black curve),
        and modelled glaciated area during the LGM (coloured curve). The LGM
        is here modelled as a time-transgressive event.}
      \label{fig:timing}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{%
        \textbf{(a)} Modelled age of maximum ice thickness (colour) and maximum
        ice surface elevation (200\,m contours) above trimline locations
        \citep[Table~1]{Kelly.etal.2004} in the upper Rhone valley.
        \textbf{(b)} Modelled maximum ice thickness against observed trimline
        elevations \citep[Table~1]{Kelly.etal.2004}.
        \textbf{(c)} Histogram of modelled maximum ice thickness above trimline
        locations (500\,m bands). The average maximum ice thickness above the
        trimline is 979\,m.
        \todo{Add cold ice areas or so. Use max
              surface elevation age as in Fig.~\ref{fig:timing}.}}
      \label{fig:trimlines}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{%
        Modelled glacier extent and thickess along selected profiles for the
        Rhine, Rhone, Ivrea and Isère glaciers.}
      \label{fig:profiles}
    \end{figure}

>>>>

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_timing}}
      \caption{%
        \textbf{(a)} Timing of the LGM given by the modelled age of maximum ice
        thickness throughout the entire simulation (colour mapping) and
        corresponding, ice surface elevation (200\,m contours).
        \textbf{(b)} Temperature offset time-series from the EPICA ice core
        used as palaeo-climate forcing for the ice flow model (black curve),
        and modelled glacierized area during the LGM (coloured curve). The LGM
        is here modelled as a time-transgressive event.}
      \label{fig:timing}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{%
        \textbf{(a)} Comparison of modelled ice surface elevation at the LGM
        (time-transgressive, corresponding to maximum ice thickness,
        Fig.~\ref{fig:timing}), compensated for bedrock deformation, against
        observed trimline elevations \citep[Table~1]{Kelly.etal.2004}. Model
        variables were bilinearly interpolated to the trimline locations.
        \textbf{(b)} Histogram of differences between modelled LGM ice surface
        elevation and trimline elevations (500\,m bands). The average
        difference is 861\,m.}
        \textbf{(c)} Modelled age of maximum ice thickness at the trimline
        locations \citep[Table~1]{Kelly.etal.2004} in the upper Rhone valley
        (colour) and LGM ice surface elevation (200\,m contours). Hatches
        mark areas modelled to have experienced less than 1\,ka temperate ice
        cover during MIS~2 (29--14\,ka).
      \label{fig:trimlines}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{%
        \textbf{(a, c, e, g)} Approximate glacier flowlines drawn by hand
        rougly following selected glacial valley centerlines.
        \textbf{(b, d, f, h)} Evolution of modelled glacier extent in time,
        bilinearly interpolated along the corresponding profiles, showing
        numerous cycles of advance and retreat over the last glacial cycle.
        Isolated patches indicate periodic surges from tributary glaciers.}
      \label{fig:profiles}
    \end{figure}
